Effect_size_families

### 2019-05-22 pollen_family.Rmd
plots of pollen ratio and total pollen modified, everything organised in pollen_family.Rmd

>>>>

\newpage

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
library(ggplot2)
total_pollen <- read.csv("Rmd/Data/total_pollen.csv")
ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
  geom_bar(stat='identity', position='dodge')+theme_minimal()+
  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")
